Constraints on the mass and occupation fraction of dark matter halos hosting Lyman-alpha emitters at $z\sim 3$

### 2013-07-09 paper/ms.tex
minor changes before lunch :)

\citep{Ouchi2010} prefers a very lowe duty cycle $0.008\pm 0.03$.

@@

In this \documentname we constrain the preferred dark matter mass
and occupation fraction for halos hosting Lyman Alpha Emitters at
redshift $z=3.1$ in a $\Lambda$CDM cosmology. We use a method that
matches the cosmic variance of the surface 
density number of LAEs between mock and real observations and is also
consistent with observational estimates for the angular
correlation function. The mock catalogs are constructed using a 
model with three basic parameters: the halo mass range where LAEs can
be found, $M_{\rm   min}<M_{\rm h}<M_{\rm   max}$, and the fraction of
the halos in this range that are actually occupied, $f_{\rm occ}$. After
a thorough exploration of the parameter space we find that wide
variety of models are consistent with the observational constraints,
where only a minority has been considered so far in the
literature. Out of $9000$ initial combinations for the model
parameters we end up with $49$ successful arrangement of parameters.

The most important conclusion of this work is that available
observational information for the clustering properties of LAEs at
$z=3.1$ does not provide enough constraints to uniquely narrow the range of masses
and occupation fraction of dark matter halos hosting those galaxies. In our
model, the hosting halos can be split into three families depending the mass range
$\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm min}$ and the
occupation fraction $f_{\rm occ}$. The first family is narrow both in
$\Delta M$ and $f_{\rm occ}$, a second family is only narrow in
$\Delta M$ and the third is narrow in $f_{\rm occ}$ and broad in
$\Delta M$.

>>>>

... \cite{Ouchi2010} prefers a very lowe duty cycle $0.008\pm 0.03$.

@@

In this \documentname we constrain the preferred mass
and occupation fraction of dark matter halos hosting Lyman Alpha Emitters at
redshift $z=3.1$ in a $\Lambda$CDM cosmology. We use a method that
matches the cosmic variance of the surface 
density number of LAEs between mock and real observations and is also
consistent with estimations of the angular
correlation function. The mock catalogs are constructed using a 
model with three basic parameters: the halo mass range where LAEs can
be found, $M_{\rm   min}<M_{\rm h}<M_{\rm   max}$, and the fraction of
the halos in this range that host a detectable LAE, $f_{\rm occ}$. After
a thorough exploration of the parameter space we find that a wide
variety of models are consistent with the observational constraints,
where only a minority has been considered so far in the
literature. Out of $9000$ initial combinations for the model
parameters we end up with $49$ successful arrangement of parameters.

The most important conclusion of this work is that available
observational information for the clustering properties of LAEs at
$z=3.1$ does not provide enough constraints to uniquely narrow the range of masses
and occupation fraction of dark matter halos hosting those
galaxies. In particular we are not able to put a stringent constraint
on the occupation fraction $f_{\rm occ}$.

In our results the models can be split into three families
depending the mass range $\Delta M=\log_{10}M_{\rm max} -
\log_{10}M_{\rm min}$ and the occupation fraction $f_{\rm occ}$. The first family is narrow both in
$\Delta M$ and $f_{\rm occ}$, a second family is only narrow in
$\Delta M$ and the third is narrow in $f_{\rm occ}$ and broad in
$\Delta M$.
